---
title: "Introduction to R"
author: "Dhiraj Saharia"
output:
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    number_sections: true
  pdf_document: default
---
-----
### Important Points
* R does not have a way to store individual variable, it does so by creating vectors of length 1.
----

### Saving Workspace session 
* Use `save(a, file="session1.Rdata")` to save a single variable `a`.
* To load data use `load(file="session1.Rdata")`.
* To save complete Workspace `save.image()` or `save(list=ls(all.names=TRUE), file="sess1.Rdata")`.

### Variables and datatypes in R
* Variable names - Start with alphabet, then Alphanumeric, '_' and '.'.
* Predefined Constants -
```{r}
pi
letters
# Letter
month.name
```

* Data Types -
  1. Logical - T/F.
  2. Integer - All Integers.
  3. Numeric - All Real Numbers.
  4. Complex - All Complex numbers.
  5. Character - 'a', 'b' ... etc

* Basic tasks regarding Data types -
  1. Data type of object - `typeof(obj)`.
  2. Verify certain data type - `is.data_type(obj)`.
  3. Cooerce data types - `as.data_type(obj)`.

* Basic objects -
  1. Vector - Collection of same data types.
  2. List - Collection of objects.
  3. Data Frame - Generic tabular object.
* Vectors -
Named Vectors can also be created.
```{r}
vector = c(one=1,two=2,three=3,four=4,five=5) # Here c() is the concatenation operator.
print(vector)
```