---
title: "Matrix operations in R"
author: "Dhiraj Saharia"
date: "08/02/2020"
output:
  html_document:
    df_print: paged
    theme: flatly
    toc: yes
    number_sections: true
---
* Matrix operations -
  1. Rectangular arrangement of numbers in rows and columns.
  2. Rows - horizontally and Columns - Vertically
  
```{r}
A = matrix(c(1,2,3,4,5,6,7,8,9), nrow = 3, ncol = 3, byrow = TRUE)
print(A)
```
* Special Matrices -
  * Scalar Matrix - All rows and columns are filled with constant `k`. `matrix(k, m, n)`.
  * Diagonal Matrix - Diagonals are filled with k or a vector. `diag(c(1,2,3), 3, 3)`.
  * Identity Matrix - Diagonals are 1. Use `diag(1, m, n)`.
  
* Matrix metrics -
 * `dim(A)` - return size of matrix.
 * `nrow(A)` - return number of rows.
 * `ncol(A)` - return number of columns.
 * `length(A)` - return number of elements.
 
* Accessing, editing and deleting in elements in matrices -
  * Same notation used as dataframes.
  * `rownames()` and `colnames()`.
```{r}
colnames(A) = c("a", "b", "c")
rownames(A) = c("e", "f", "g")
print(A)
```
  * Accessing an entry in the matrix -
  * `A[2,3]` - 2nd row and 3rd column.
  * `A[,3]` - Third column only. and `A[2,]` - Row two only.
  * `A[,-2]` - Everything except the second column.

* Colon Operator -
  * Used to pick sub-matrices.
  * `A[1:3, 1:2]` - Rows 1,2 and 3 with columns 1 and 2.
  * `A[c(1,3), 1:2]` -  Rows 1 and 3 with columns 1 and 2.
  
* Matrix Concatenation -


  
